Toward dynamic models of combat or lack thereof in animal mating

### 2016-01-11 ms.tex
small change to abandon

/* this is just for consideration I am not sure if it will be needed or useful */
Number of mature males at time $t$:
\begin{equation} \label{eq:num_mature}
    K_{mature}(t) = \lfloor{K_{initial}(Pr({\rm mature} \, | m(t)) - S(t))}\rfloor
\end{equation}
A searching individual has a chance to encounter a nest equal to its ``exploration trait'' $\lambda_i$:
\begin{equation} \label{eq:encounter probability}
    Pr({\rm Encounter}) = \lambda_i
\end{equation}
The number of encounters that a searching individual has engaged in is:
\begin{equation} \label{eq:encounter rate}
    {\rm Encounters} = \lfloor\lambda_i \cdot t_{searching}\rfloor
\end{equation}
the average exploration trait across a cohort is $\bar\lambda$.

similarly for males abandoning nests males the probability of abandoning a nest $j$, is a function of the  the reproductive value of the nest $R_j$ and the abandon trait of the individual $\psi_i$:

assumption: $1 < R_j$, $0 < \psi_i < 1$

>>>>

/* this is just for consideration I am not sure if it will be needed or useful */\\ \\
Number of mature males at time $t$:
\begin{equation} \label{eq:num_mature}
    K_{mature}(t) = \lfloor{K_{initial}(Pr({\rm mature} \, | m(t)) - S(t))}\rfloor
\end{equation}
A searching individual has a chance to encounter a nest equal to its ``exploration trait'' $\lambda_i$:
\begin{equation} \label{eq:encounter probability}
    Pr({\rm Encounter}) = \lambda_i
\end{equation}
The number of encounters that a searching individual has engaged in is:
\begin{equation} \label{eq:encounter rate}
    {\rm Encounters} = \lfloor\lambda_i \cdot t_{searching}\rfloor
\end{equation}
the average exploration trait across a cohort is $\bar\lambda$.

Similarly for males abandoning nests males the probability of abandoning a nest $j$, is a function of the  the reproductive value of the nest $R_j$ and the abandon trait of the individual $\psi_i$:

assumption: $1 < R_j$,  $1 < \psi_i$
